Proofs as Programs in Classical Logic\\Notes

### 2021-11-16 Notes/notes.tex
Plan

>>>>

\section{Plan}

Goal:
\begin{itemize}
	\item Extract program from resolution proofs of $\forall\exists$-sentences over inductive datatypes.
\end{itemize}

\noindent Steps:

\begin{itemize}
	\item Give extensions of G\"odel's System \textbf{T} and HAS + EM$_1$ + SK$_1$ to arbitrary inductive datatypes (possibly GADTs) and prove (or rather check) properties, i.e. strong normalization, cut-elimination, uniqueness of normal forms.
	\item Adapt the results of~\cite{aschieri2014interactive} to exhibit realizers in $\mathcal{F} + \Phi$ for cut-free proofs in the extended version of HAS + EM$_1$ + SK$_1$ of formulas $\forall x\exists y Pxy$ where $P$ is a predicate in the extended version of \textbf{T}.
	\item Adapt the iterative learning from~\cite{aschieri2014interactive} to extract $\lambda$-terms from realizers.
	\item Give a proof translation from resolution proofs to cut-free sequent calculus proofs (already done?).
\end{itemize}

\noindent Questions:
\begin{itemize}
	\item When does the translated proof require more than EM$_1$?
	\item Using the methods in~\cite{aschieri2014interactive} the extracted term will be in simple $\lambda$-calculus. Is is possible to obtain a term in $\mathcal{F}$? (Talk with Federico Aschieri)
	\item Can the predicates be defined in $\mathcal{F}$ instead of $\mathcal{T}$? (probably yes)
	\item What happens if we add non-inductive theories?

\end{itemize}

\pagebreak
